Transformation of forecasts for evaluating predictive performance in an epidemiological context

### 2023-06-21 reply_to_reviews.tex

Thank you for your thorough and extensive comments.

We added the following to the discussion to make our intentions clearer regarding the preferences of policy makers:

\indented
In this paper, we did not make any particular assumptions about policy makers' priorities and preferences. Rather, we aimed to enable users to make an informed choice by showing how different transformations lead to different relative weights for the kinds of prediction errors forecast consumers may care about, such as absolute vs. relative errors or the size of penalties for over- vs. underprediction. In practice, engagement with decision makers is important to determine what their priorities are and how different ways to measure predictive importance should be weighed.

\notindented
It is important to note that changing the relative weight for different times and locations is one effect of the scoring forecasts on the log scale, but not necessarily the main point of the transformation. Rather, we do recommend to evaluate forecasts on the log scale as we believe the interpretation as a score of the exponential growth rate is meaningful in an epidemiological context. As stated explicitly in the manuscript, we moreover recommend to use this in complement to rather than as a replacement of the common evaluation on the ``natural scale''. Evaluators will then become aware of whether their results depend strongly on this decision and the implied weighting of different forecasting tasks.

@@

\blue
\subsection{Major comments}

``Natural logarithm'', log1p, and log($a + x$) are conflated in several places, despite the discussion in Section 2.4 noting that this is an important distinction. The terminology should not be overloaded. (E.g., L20 ``Applying the log transformation''.)

\black
We changed ``Applying the log transformation'' to ``Applying a transformation of log($x + 1$)'' in L20 (in the abstract).

We slightly disagree with the notion that the terminology should not be overloaded. Not introducing another term for transformations of $\log_{e}(x + \varepsilon)$ makes the manuscript more readable and accessible to readers. In addition, our analyses suggest that adding a small offset doesn't make much of a difference in most practical applications. We nevertheless completely agree that this should be made clear to the reader and have added the following text:

@@

\indented
The assumption of a quadratic mean-variance relationship is closely linked to the aspects discussed in Sections 2.1 and 2.2. It implies that relative errors have constant variance and can thus be meaningfully compared across different targets. Also, it arises naturally if we assume that our capacity to predict the epidemic growth rate does not depend on the expected outcome, i.e. does not depend on the current phase of the epidemic or the order of magnitude of current observations.

\notindented

\blue
L150: “it may be desirable” — Is it though? This seems unlikely. Stakeholders likely want to emphasize some locations and times over others, and would benefit from some rules about how to do so while maintaining propriety. (E.g., is scaling by some function of recent observations or the population size okay? Is scaling by the forecast or observed value okay? Or are we limited to monotonic transformations?)

\black
We think that while it is certainly not the only relevant approach, there is a case to be made for an evaluation which gives each forecasting target a similar weight. This is attractive if the goal of the evaluation is to find the best forecasting model for future use and if one assumes that the difficulty of the forecasting task is similar in different locations. Take for example two models that make independent forecasts for cases of COVID-19 in Germany, Luxembourg and Liechtenstein. CRPS scores on the natural scale would be dominated by the predictive performance in Germany. One model could be a lot better in Luxembourg and Liechtenstein and slightly worse in Germany and end up looking worse in terms of overall CRPS. However, it is unclear whether predictive performance in Germany really provides e.g. 100 times more information about how good a model is at predicting disease dynamics. If the question is which model to deploy in another location in the future, then it might be desirable to not have average scores be dominated by a single location.

@@

This illustrates that a quadratic mean-variance relationship can arise from a simple yet not completely unreasonable renewal equation model.

% to model epidemiological processes. We agree with the reviewer that a size parameter of 0.1 is not realistic, but still think that the example is valuable as an illustration.

\blue
Figure 3: is a geometric distribution realistic for epidemiological surveillance data?

\black
We agree that this is not a typical example we would expect to see in an epidemiological setting. It could happen in principle, but only in rather constructed cases. We still believe the example is valuable to illustrate the general point that the rankings between two forecasts can change even for a single observation. We added the following sentence:

\indented
We note that the chosen example involving a geometric forecast distribution is somewhat constructed; as shown in Section \ref{sec:Hub:cor} and Figure \ref{fig:HUB-cors}A, rankings between models usually stay quite stable for a single forecast. .

@@

\blue
L99: How are atoms at $\exp x = 0$ handled? How are observations of $y = 0$ handled?

\black
In the theoretical discussion in Section 2 we defined prediction targets to have strictly positive support, so these cases are excluded. In the later parts we follow the common strategy to add an offset before taking the logarithm.

\blue

L127: “approximation of the absolute percentage error” — Raises a few questions:
\begin{itemize}
    \item If a relative error metric is desired, why not just divide CRPS/WIS by y then? (Propriety?)\\
    \black
Yes, dividing by the observed value generally disturbs propriety. This approach would correspond to weighting CRPS scores with weights depending on the observed value, and it has been shown that the resulting average scores are no longer proper; see Lerch et al (2017, Statistical Science, preprint: \url{https://arxiv.org/abs/1512.09244})
    \item \blue How does using a (shifted) log transform differ from dividing by (a constant plus) (a mean of) the most recent observation(s)?\\
    \black Like in the related arguments in the paper we address this question for the simpler case of the absolute error rather than CRPS. Using a shifted log transform corresponds to (in slight variation of equation (8))
    \begin{equation}
    |\varepsilon^*_t| = |\log (\hat{y_t} + a) - \log(y_t + a)| = \left|\log\left(\frac{\hat{y}_t + a}{y_t + a}\right) \right| \ \ \stackrel{\text{if } \hat{y}_t \ \approx \ y_t}{\approx} \ \ \left| \frac{\hat{y}_t + a}{y_t + a} - 1 \right| \ \ = \ \ \left| \frac{\hat{y}_t - y_t}{y_t + a} \right|.
    \end{equation}
    Dividing by the last observation plus a constant $a$, on the other hand, corresponds to
    \begin{equation}
    |\varepsilon^*_t| = \left|\frac{\hat{y}_t + a}{y_{t - 1} + a} - \frac{y_t + a}{y_{t - 1} + a} \right| = \ \ \left| \frac{\hat{y}_{t - 1} - y_t}{y_{t - 1} + a} \right|.
    \end{equation}
    If we interpret the denominator as an (inverse) weight for the different absolute errors, log transformation thus corresponds approximately equivalent to weighting with the inverse new observation $y_t$ (though better behaved in terms of the resulting incentives). Dividing by the previous value corresponds to weighting with the inverse preceding observation. As autocorrelation is typically strong in the time series we consider, this will yield similar, but not identical results.\\
    In terms of the epidemiological  interpretation, dividing by the last observed value can be interpreted as a score for a multiplicative, rather than an exponential growth rate. % We haven't investigated in detail how the two differ in their behaviour, but would expect them to yield mostly similar results. 
    \item \blue Is this desired? Though already discussed, seems like the major point of doubt here: are we at risk of overemphasizing very-low-activity periods and very-low-population states where standard-deviation-to- mean ratios are much higher?\\
    \black We agree that it may be an issue in practice that low-activity-periods could get overemphasised and therefore believe that an evaluation should show both scores on the natural scale as well as on the log scale. 
\end{itemize}

@@

We added a reference to this source. We nonetheless agree with the referee that this approximation will work best if the distribution is tight and added a short remark to this regard.

The current paragraph reads:

\indented

If the mean-variance relationship of the data-generating distribution is quadratic with $\sigma^2 = c \times \mu^2$, the natural logarithm can serve as the VST \citep{guerreroTimeseriesAnalysisSupported1993}. Denoting by $F_{\log}$ the predictive distribution for $\log(Y)$, we can use the delta method (a first-order Taylor approximation, see e.g., \citealt{Dunn2018}), to show that

@@

\black
I'm not sure I can follow. In my mind the plot is there to show you that once your values are like 5 times larger than the offset you choose than the offset doesn't have much of an effect. So it's designed to show that for most practical purposes, doing log(x + a) should be mostly equivalent to log(x). So to me it's less about choosing an appropriate a and more about showing that probably it's just fine to go with some random small a. I think Figure SI.7 is more about "choosing an a".

\blue
Figure SI.7:
\begin{itemize}
    \item Also specify sorting variable\&direction on x axis. (Would a point plot vs. the sorting variable be more informative?)
    \item Very informative figure, promote to main text? Also would like to see for different “parts” of an epidemic (e.g., steady low periods, increases, peaks/plateaus, decreases). Deaths figures suggest that balancing scores between locations can be tricky, and both cases and deaths suggests that the investigated transformations can’t do this exactly.
\end{itemize}

\black
We added a statement to the legend "Locations are sorted according to the mean observed value in that location." We also followed your suggestion to make this a main figure.

We would expect that one could find a value for a that would eventually yield a more or less flat line, but we haven't investigated this in practice.

### 2023-06-21 reply_to_reviews.tex

\newcommand{\red}{\color{red}}
\newcommand{\black}{\color{black}}
\newcommand{\blue}{\color{blue}}

\newcommand{\indented}{\setlength{\leftskip}{1cm}}
\newcommand{\notindented}{\setlength{\leftskip}{0cm}}

\begin{document}

%\black \textbf{Black: our comments}
%\red \textbf{Reviewer, not addressed}
%\blue \textbf{Reviewer, addressed}

@@

We added the following to the discussion to make our intentions clearer regarding the preferences of policy makers:

\indented
In this paper, we did not make any particular assumptions about policy makers' priorities and preferences. Rather, we aimed to enable users to make an informed choice by showing how different transformations lead to different relative weights for the kinds of prediction errors forecast consumers may care about, such as absolute vs. relative errors or the size of penalties for over- vs. underprediction. In practice, engagement with decision makers is important to determine what their priorities are and how different ways to measure predictive importance should be weighed.

\notindented
It is important to note that changing the relative weight for different times and locations is one effect of the scoring forecasts on the log scale, but not necessarily the main point of the transformation. Rather, we do recommend to evaluate forecasts on the log scale as we believe the interpretation as a score of the exponential growth rate is meaningful in an epidemiological context. As stated explicitly in the manuscript, we moreover recommend to use this in complement to rather than as a replacement of the common evaluation on the ``natural scale''. Evaluators will then become aware of whether their results depend strongly on this decision and the implied weighting of different forecasting tasks.

Users who are explicitly concerned about the relative weights of different times and locations can e.g. find information in Figure 3 where we show how different forecast targets are emphasized by evaluation on the natural or log-transformed scale. A user could e.g. reproduce such a display with different values of the offset $a$ and choose $a$ such that the relative weighting of times and regions with high and low incidence correspond to their preferences.

\blue
Additionally, any additional necessary/recommended elements of a scoring procedure should be noted more prominently (e.g., dealing with forecast missingness, outlying forecasts, outlying data, selecting a Box-Cox transformation, selecting a shift ($a$ value), etc.).

@@

\black

To direct the readers' attention to the mentioned challenges already in the conceptual part of the paper we added the following paragraph to Section 2.4, which also contains a discussion of the choice of $a$:

\indented
We note that in the practical evaluation of operational forecasting systems  several additional challenges arise, which we do not study in detail. These concern e.g., the removal of outlying observations and forecasts and the handling of missing forecasts. The solutions we employed in practice are provided in Section 3.1.
\notindented

We agree that it would be useful to have a more thorough discussion of all the considerations involved in evaluating forecasts, but feel this is slightly beyond the scope of this paper.

@@

This illustrates that a quadratic mean-variance relationship can arise from a simple yet not completely unreasonable renewal equation model.

\blue
Figure 3: is a geometric distribution realistic for epidemiological surveillance data?

\black
We agree that this is not a typical example we would expect to see in an epidemiological setting. It could happen in principle, but only in rather constructed cases. We still believe the example is valuable to illustrate the general point that the rankings between two forecasts can change even for a single observation. We added the following sentence:

\indented
We note that the chosen example involving a geometric forecast distribution is somewhat constructed; as shown in Section 3.4 and Figure 8A, rankings between models usually stay quite stable for a single forecast. .

@@

\notindented

\blue
L236: “better able to illustrate the effects” — Why does this removal help illustrate the effects? Is such a removal procedure required to be able to apply this transformation approach at all? And if so, what are the requirements/considerations for such a removal procedure?

\black
We updated the paragraph as follows:

\indented
In addition, we filtered out erroneous forecasts that were in extremely poor agreement with the observed data, as defined by any of the conditions listed in Table SI.2. Figure SI.6 shows the percentage of forecasts removed for each model. Those few (less than 0.2\%  of forecasts for each model) erroneous outlier forecasts had excessive influence on average scores and relative skill scores in a way that was not representative of normal model behaviour. We removed them here in order to better illustrate the effects of the log-transformation on scores that one would expect in a well-behaved scenario. In a regular forecast evaluation such erroneous forecasts should usually not be removed and would count towards overall model scores.

@@

\notindented

\blue
L244: “pairwise comparisons” — The necessity of using an approach to handle missingness when combining evaluations should be noted more prominently from the beginning. The same applies to the outlier removal (if necessary) and a value selection.

@@

\black
We think that this is entirely up to the stakeholders and may depend on the setting. We hope that the reasoning and trade-offs involved become sufficiently clear throughout the remainder of the paper.

\blue
L15 “log-transformed counts” — Immediately sounds problematic due to the possibility of 0 counts, without mention of a shift or threshold. Additionally, there is a truncated normal distribution in the mix; is it rounded to counts, or are these not all count data?

\black
We changed "log-transformed counts" to "log-transformed values" and updated the abstract to point out that we're applying a transformation of log($x + 1$) to our example data:

\indented
Applying a transformation of log(x + 1) to data and forecasts from the European COVID-19 Forecast Hub

@@

The truncated normal distribution used as an example in Figure 2 is based directly on samples from the normal distribution, so here no rounding was applied.

\blue
L23–L24 “more strongly emphasized”, “less severely penalized” — Could note that this is relative to evaluations on the natural scale (not relative to each other).

\black
Thank you for the suggestion. We updated the abstract as such:

\indented
Situations in which models missed the beginning of upward swings are more strongly emphasised while failing to predict a downturn following a peak is less severely penalised when scoring transformed forecasts as opposed to untransformed ones.

@@

\black
The weighted interval score is a weighted sum of interval scores for the individual prediction intervals. When weighing the individual interval scores for the central $1 - \alpha$ prediction intervals by 
$w = \alpha / 2$ (which is generally standard), then the WIS converges exactly to the CRPS for an increasing number of equally spaced prediction intervals. For an illustration see Figure 2 in \cite{bracherEvaluatingEpidemicForecasts2021}.

\blue
L59 “strength” — The meaning of “strength” is nonintuitive without reading the citation and understanding the ties to multiplicative interventions on R and r (the latter of which seems unrealistic to achieve). Consider surrounding with quotes, explaining more/less, relating to growth per generation, etc.

\black
We updated the sentence to make this clearer. The new sentence is now:

\indented
The reproduction number $R$ describes the number of people each infected person is expected to infect in turn (irrespective of the time between infections) and therefore is a measure of the strength of epidemic growth. The growth rate $r$ describes the speed of epidemic growth.

@@

L138: “$\Bar{r}$ is” — Consider $\Bar{r}_t$ etc.

L146: “$\Bar{\hat{r}}$” — Should be $\hat{\Bar{r}}$, or consider $\hat{\Bar{r}}_t$.

\black
We applied the suggested changes.

\blue
L158 “delta method” — Delta method would seem to also require the distribution to be somewhat tightly distributed, concentrated within a nearly-linear region of the transformation function. But putting significant mass on a wider range of values would also mean having non-negligible mass on negative values if “approximately normal”; it would not make sense to apply the logarithm or sqrt transformations in these cases. So perhaps the “tightly distributed” assumption can be taken. But this seems a bit nonobvious and a justification/application of the delta method would be helpful here.

@@

\black

This argument is a common justification for the choice of variance-stabilizing transformations, see e.g., the below excerpt from \textit{Generalized Linear Models With Examples in R} by Dunn and Smyth:
\begin{quote}
Suppose that $y$ has a mean-variance relationship defined by the function $V(\mu)$, with $\text{var}(y) = \phi V(\mu)$. Then, consider a transformation $y^* = h(y) \approx h(\mu) + h'(\mu)(y - \mu)$, from which it can be inferred that
$$
\text{var}(y^*) = \text{var}[h(y)] \approx h'(\mu)^2\text{var}(y).
$$
Hence, the transformation $y^* = h(y)$ will approximately stabilize the variance if $h'(\mu)$ is proportional to $\text{var}(y)^{-1/2} = V(\mu)^{-1/2}$. When $V(\mu) = \mu^2$ [...], the variance-stabilizing transformation is the logarithm, because then $h'(\mu) = 1/\mu$.  When $V(\mu) = \mu$, the variance-stabilizing transformation is the square root because $h'(\mu) = 1/\mu^{1/2}$.
\end{quote}

We added a reference to this source. We nonetheless agree with you that this approximation will work best if the distribution is tight and added a short remark to this regard.

@@

If the mean-variance relationship of the data-generating distribution is quadratic with $\sigma^2 = c \times \mu^2$, the natural logarithm can serve as the VST \citep{guerreroTimeseriesAnalysisSupported1993}. Denoting by $F_{\log}$ the predictive distribution for $\log(Y)$, we can use the delta method (a first-order Taylor approximation, see e.g., \citealt{Dunn2018}), to show that

\begin{equation}
\mathbb{E}_F[\text{CRPS}\{F_{\log}, \log(y)\}] \approx \frac{\sigma/\mu}{\sqrt{\pi}} 
= \frac{\sqrt{c}}{\sqrt{\pi}}
.
\end{equation}

The addition on ``tightly distributed'' probability mass reads

\indented
We note that while standard in the derivation of variance-stabilizing transformations, the application of the delta method in equations (16) and (17) requires the probability mass of $F$ to be tightly distributed. If this is not the case, the approximation may be less accurate.

@@

\blue
Figure 5 caption:
\begin{itemize}
    \item “logarithmic” — With what a values? (THe first link to Figure 5 is from before this information was stated.)
    \item “D: [. . . ] all individual scores” — of EuroCOVIDhub-ensemble or any of the 7 included systems?
    \item “relative change” — of what change in scores relative to what quantity?
\end{itemize}

\black
We have updated the caption, which now reads:

\indented
Scores for two-week-ahead forecasts from the EuroCOVIDhub-ensemble (averaged across all forecast dates) for different locations, evaluated on the natural scale as well as after transforming counts by adding one and applying the natural logarithm. D: Corresponding boxplots of all individual scores of the EuroCOVIDhub-ensemble for two-week-ahead predictions. E: Boxplots for the relative change of scores for the EuroCOVIDhub-ensemble across forecast horizons. For any given forecast date and location, forecasts were made for four different forecast horizons, resulting in four scores. All scores were divided by the score for forecast horizon one. To enhance interpretability, the range of visible relative changes in scores (relative to horizon = 1) was restricted to [0.1, 10].

\blue
L272: “with the standard deviation” — Also note here that this is for approximately normal data distributions?

@@

\black
We slightly adapted the text to make this point clearer:

\indented
It is possible to go beyond choosing a single transformation by constructing composite scores as a weighted sum of scores based on different transformations. This would make it possible to create custom scores and allow forecast consumers to choose and assign explicit weights to different qualities of the forecasts they might care about.

\notindented

\blue
Figure SI.2: Would benefit from some more discussion, and perhaps a plot of slightly different quantities. E.g., to select an appropriate value of a, it seems like a common goal would be to deprioritize errors around values of x low enough that we expect there to be primarily noise rather than signal or that are not of concern to policymakers. For count data, this likely includes the values 0 - -10 in any circumstances; how far beyond 10 this range extends depends on the range of realistic growth rates, the forecast horizon, and cleanliness of the data. To assist in this decision, it seems like a similar plot of the evaluations of a particular absolute and/or relative error might be useful, or discussion of how to read it from the current plot. E.g., to illustrate that the same relative error is penalized roughly the same for all the plotted values of a for values of x above 50, but quite differently for $a = 10$ vs. $a = 0.1$ for values of x near 1.

We added some more explanation to the caption of Figure SI.2. This makes the trade-off involved in choosing a suitable $a$ value clearer, without prescribing a 'correct' solution.

\indented
For a given solid line, the dashed line of the same colour marks the x-value that  is equal to 5 times the corresponding offset. It can be seen that for $a$ values smaller than one fifth of the transformed quantity, the effect of adding an offset is generally small. When choosing a suitable $a$, the trade-off is between staying close to the interpretation of a pure log-transformation (choosing a small $a$) and not giving excessive weights to small observations (by choosing a larger $a$, see Figure 3).

### 2023-06-21 main.tex
address more reviewer comments

\begin{linenomath*}
\begin{equation}
\mathbb{E}_F[\text{CRPS}\{F_{\log}, \log(y)\}] \approx \frac{\sigma/\mu}{\sqrt{\pi}} 
= \frac{\sqrt{c}}{\sqrt{\pi}}
.\label{eq:taylor_quadratic}
\end{equation}
\end{linenomath*}
As $\sigma$ and $\mu$ are linked through the quadratic mean-variance relationship ($\sigma = \sqrt{c} \times \mu$), the expected CRPS stays constant regardless of the expeccted value of the data-generating distribution $\mu$. The assumption of a quadratic mean-variance relationship is closely linked to the aspects discussed in Sections \ref{sec:methods:relative} and \ref{sec:methods:growthrate}. It implies that relative errors have constant variance and can thus be meaningfully compared across different targets. Also, it arises naturally if we assume that our capacity to predict the epidemic growth rate does not depend on the expected outcome, i.e. does not depend on the current phase of the epidemic or the order of magnitude of current observations.

@@

Transformations that are strictly monotonic are permissible in the sense that resulting scores remain proper. This is because even though rankings of models may change forecasts will in expectation still minimise their score if they report a predictive distribution that is equal to the data-generating distribution. This condition holds for both the log and square root transformations, as well as many others. However, the order of the operations matters, and applying a transformation after scores have been computed generally does not guarantee that the score remains proper. In the case of log transforms, taking the logarithm of the scores, rather than scoring the log-transformed forecasts and data, results in an improper score. We illustrate this point using simulated data in Figure \ref{fig:log-improper}, where it can be seen that in the example overconfident models perform best in terms of the log WIS.

In practice, one issue with the log transform is that they are not readily applicable to negative numbers or zero values, which need to be removed or otherwise handled. 
One common approach to deal with zeros is to add a small quantity, such as 1, to all observations and predictions before taking the logarithm \citep{bellegoDealingLogsZeros2022}. This represents a strictly monotonic transformation and therefore guarantees that the resulting score remains proper. The choice of the quantity to add does however influence scores and rankings, as measures of relative errors shrink when adding a constant $a$ to the forecast and the observation. We illustrate this in Figure \ref{fig:illustration-effect-log-offset}. As a rule of thumb, if if $x > 5a$, the difference between $\log{(x + a)}$ and $\log{(x)}$ is small, and it becomes negligible if $x > 50a$. Choosing a suitable offset $a$ balances two competing concerns: on the one hand, choosing a small $a$ makes sure that the transformation is as close to a natural logarithm as possible and scores can be interpreted as outlined above. On the other hand, choosing a larger $a$ can help stabilise scores for forecasts and observations close to zero, avoiding giving excessive weight to forecasts for small quantities (see Figure \ref{fig:HUB-log-different-offsets}). For large values of $a$, $\log(x + a)$ grows linearly in $x$, meaning that we expect to observe the same patterns as in the case with no transformation. For decreasing values of $a$, we give more relative weight to scores in small locations.

@@

.

@@

The forecasts used for the purpose of this illustration are forecasts submitted between the 8th of March 2021 and the 5th of December 2022 for reported cases and deaths from COVID-19. Target dates range from the 13th of March 2021 to the 10th of December 2022, for a total of 92 weeks. See \cite{sherrattPredictivePerformanceMultimodel2022} for a more thorough description of the data. We filtered all forecasts submitted to the Hub to only include the seven models which have submitted forecasts for both deaths and cases for 4 horizons in 32 locations on at least 46 forecast dates (see Figure \ref{fig:HUB-num-avail-models}). We removed all observations marked as data anomalies by the European Forecast Hub \citep{sherrattPredictivePerformanceMultimodel2022} as well as all remaining negative observed values. These anomalies made up a relevant fraction of all observations. On average across locations, 12.1 out of 92 (13.2\%) observations were removed for cases and 12.4 out of 92 (13.5\%) for deaths. Figure \ref{fig:number-anomalies} displays the number of anomalies removed for each location. In addition, we filtered out a small number of erroneous forecasts that were in extremely poor agreement with the observed data, as defined by any of the conditions listed in Table \ref{tab:erroneous}. Figure \ref{fig:erroneous-forecasts.png} shows the percentage of forecasts removed for each model. Those few (less than 0.2\%  of forecasts for each model) erroneous outlier forecasts had excessive influence on average scores and relative skill scores in a way that was not representative of normal model behaviour. We removed them here in order to better illustrate the effects of the log-transformation on scores that one would expect in a well-behaved scenario. In a regular forecast evaluation such erroneous forecasts should usually not be removed and would count towards overall model scores.

@@

The log-transformation is only one of many transformations that may be useful and appropriate in an epidemiological context. One obvious option is to apply a population standardization to obtain incidence forecasts e.g., per 100,000 population \citep{abbottEvaluatingEpidemiologicallyMotivated2022}. 
We suggested using the natural logarithm as a variance-stabilising transformation (VST). This is appropriate for variables that are approximately normally distributed and have a quadratic mean-variance relationship with $\sigma^2 = c \times \mu^2$ (this is e.g. approximately true for the negative binomoial distribution and large $\mu$). Alternatively, the square-root transformation can be appropriate in the case of a Poisson distributed variable \citep{dunnGeneralizedLinearModels2018}. Other VST like the Box-Cox \citep{boxAnalysisTransformations1964} are conceivable as well.
If one is interested in multiplicative, rather than exponential growth rates, one could convert forecasts into forecasts for the multiplicative growth rate by dividing numbers by the last value that was observed at the time the forecast was made. Forecasters would then implicitly predict a separate multiplicative growth rate from today to horizon 1, 2, etc. 
Instead of dividing by the last observed value, another promising transformation would be to divide each forecast by the forecast of the previous week (and analogously for observations), in order to obtain forecasts for week-to-week growth rates. Alternatively, one could also take first differences of values on the log scale. This approach would be akin to evaluating the shape of the predicted trajectory against the shape of the observed trajectory \citep[for a different approach to evaluating the shape of a forecast, see][]{srivastavaShapebasedEvaluationEpidemic2022}. Dividing values by the previous value, unfortunately, is not feasible under the current quantile-based format of the Forecast Hubs, as the growth rate of the $\alpha$-quantile may be different from the $\alpha$-quantile of the growth-rate. However, it may be an interesting approach if predictive samples are available or if quantiles for weekwise growth rates have been collected. Potentially, the variance stabilising time-series forecasting literature may be a useful source of other transformations for various forecast settings.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/illustration-effect-offset-log.png}
    \caption{Illustration of the effect of adding a small quantity to a value before taking the natural logarithm. For increasing x, all lines eventually approach the black line (representing a transformation with no offset applied).
    For a given solid line, the dashed line of the same colour marks the x-value that  is equal to 5 times the corresponding offset.}
    \label{fig:illustration-effect-log-offset}
\end{figure}

>>>>

\begin{linenomath*}
\begin{equation}
\mathbb{E}_F[\text{CRPS}\{F_{\log}, \log(y)\}] \approx \frac{\sigma/\mu}{\sqrt{\pi}} 
= \frac{\sqrt{c}}{\sqrt{\pi}}
.\label{eq:taylor_quadratic}
\end{equation}
\end{linenomath*}
As $\sigma$ and $\mu$ are linked through the quadratic mean-variance relationship ($\sigma = \sqrt{c} \times \mu$), the expected CRPS stays constant regardless of the expected value of the data-generating distribution $\mu$. The assumption of a quadratic mean-variance relationship is closely linked to the aspects discussed in Sections \ref{sec:methods:relative} and \ref{sec:methods:growthrate}. It implies that relative errors have constant variance and can thus be meaningfully compared across different targets. Also, it arises naturally if we assume that our capacity to predict the epidemic growth rate does not depend on the expected outcome, i.e. does not depend on the current phase of the epidemic or the order of magnitude of current observations.

@@

Transformations that are strictly monotonic are permissible in the sense that resulting scores remain proper. This is because even though rankings of models may change forecasts will in expectation still minimise their score if they report a predictive distribution that is equal to the data-generating distribution. This condition holds for both the log and square root transformations, as well as many others. 
Some strictly monotonic transformations that can generally be applied are scaling by the population size or scaling by past observations. This, as discussed in Section \ref{sec:discussion}, is similar to applying a log-transformation, but corresponds to evaluating a forecast of multiplicative, rather than exponential growth rates. There may of course be exceptions such as dividing by zero, but otherwise this just represents a monotonic transformation and the remaining score is still proper. Scaling a forecast by the later observed value (as opposed to scaling by past observations) is generally not permissible as it disturbs propriety (see \cite{lerchForecasterDilemmaExtreme2015} on the closely related topic of weighting scores with a function of the observed value). Similarly, scaling a forecast by predictions made by other forecasters may result in improper scores, but we are unaware of existing theoretical arguments. Scaling scores, e.g. dividing a score by the mean score for other forecasters may be acceptable in most applied settings, but we are unaware of existing theoretical arguments that could define exactly when and how this could result in improper scores (as is the case for example when dividing by zero).

When applying a transformation, the order of the operations matters, and applying a transformation after scores have been computed generally does not guarantee that the score remains proper. In the case of log transforms, taking the logarithm of the scores, rather than scoring the log-transformed forecasts and data, results in an improper score. We illustrate this point using simulated data in Figure \ref{fig:log-improper}, where it can be seen that in the example overconfident models perform best in terms of the log WIS.

In practice, one issue with the log transform is that they are not readily applicable to negative numbers or zero values, which need to be removed or otherwise handled. 
One common approach to deal with zeros is to add a small quantity, such as 1, to all observations and predictions before taking the logarithm \citep{bellegoDealingLogsZeros2022}. This represents a strictly monotonic transformation and therefore guarantees that the resulting score remains proper. The choice of the quantity to add does however influence scores and rankings, as measures of relative errors shrink when adding a constant $a$ to the forecast and the observation. We illustrate this in Figure \ref{fig:illustration-effect-log-offset}. As a rule of thumb, if if $x > 5a$, the difference between $\log{(x + a)}$ and $\log{(x)}$ is small, and it becomes negligible if $x > 50a$. Choosing a suitable offset $a$ balances two competing concerns: on the one hand, choosing a small $a$ makes sure that the transformation is as close to a natural logarithm as possible and scores can be interpreted as outlined above. On the other hand, choosing a larger $a$ can help stabilise scores for forecasts and observations close to zero, avoiding giving excessive weight to forecasts for small quantities (see Figure \ref{fig:HUB-log-different-offsets}). For large values of $a$, $\log(x + a)$ grows linearly in $x$, meaning that we expect to observe the same patterns as in the case with no transformation. For decreasing values of $a$, we give more relative weight to scores in small locations. In principle, a user could produce a plot similar to Figure \ref{fig:HUB-log-different-offsets} with different values of the offset $a$ and choose $a$ such that the relative weightings of times and regions with high and low incidence correspond to their preferences.

@@

@@

The forecasts used for the purpose of this illustration are forecasts submitted between the 8th of March 2021 and the 5th of December 2022 for reported cases and deaths from COVID-19. Target dates range from the 13th of March 2021 to the 10th of December 2022, for a total of 92 weeks. See \cite{sherrattPredictivePerformanceMultimodel2022} for a more thorough description of the data. We filtered all forecasts submitted to the Hub to only include the seven models which have submitted forecasts for both deaths and cases for 4 horizons in 32 locations on at least 46 forecast dates (see Figure \ref{fig:HUB-num-avail-models}). We removed all observations marked as data anomalies by the European Forecast Hub \citep{sherrattPredictivePerformanceMultimodel2022} as well as all remaining negative observed values. These anomalies made up a relevant fraction of all observations. On average across locations, 12.1 out of 92 (13.2\%) observations were removed for cases and 12.4 out of 92 (13.5\%) for deaths. Figure \ref{fig:number-anomalies} displays the number of anomalies removed for each location. In addition, we filtered out a small number of erroneous forecasts that were in extremely poor agreement with the observed data, as defined by any of the conditions listed in Table \ref{tab:erroneous}. Figure \ref{fig:erroneous-forecasts} shows the percentage of forecasts removed for each model. Those few (less than 0.2\%  of forecasts for each model) erroneous outlier forecasts had excessive influence on average scores and relative skill scores in a way that was not representative of normal model behaviour. We removed them here in order to better illustrate the effects of the log-transformation on scores that one would expect in a well-behaved scenario. In a regular forecast evaluation such erroneous forecasts should usually not be removed and would count towards overall model scores.

@@

The log-transformation is only one of many transformations that may be useful and appropriate in an epidemiological context. One obvious option is to apply a population standardization to obtain incidence forecasts e.g., per 100,000 population \citep{abbottEvaluatingEpidemiologicallyMotivated2022}. 
We suggested using the natural logarithm as a variance-stabilising transformation (VST). This is appropriate for variables that are approximately normally distributed and have a quadratic mean-variance relationship with $\sigma^2 = c \times \mu^2$ (this is e.g. approximately true for the negative binomoial distribution and large $\mu$). Alternatively, the square-root transformation can be appropriate in the case of a Poisson distributed variable \citep{dunnGeneralizedLinearModels2018}. Other VST like the Box-Cox \citep{boxAnalysisTransformations1964} are conceivable as well.
If one is interested in multiplicative, rather than exponential growth rates, one could, instead of applying a log transformation, convert forecasts into forecasts for the multiplicative growth rate by dividing numbers by the last value that was observed at the time the forecast was made. Forecasters would then implicitly predict a separate multiplicative growth rate from today to horizon 1, 2, etc. 
Instead of dividing by the last observed value, another promising transformation would be to divide each forecast by the forecast of the previous week (and analogously for observations), in order to obtain forecasts for week-to-week growth rates. Alternatively, one could also take first differences of values on the log scale. This approach would be akin to evaluating the shape of the predicted trajectory against the shape of the observed trajectory \citep[for a different approach to evaluating the shape of a forecast, see][]{srivastavaShapebasedEvaluationEpidemic2022}. Dividing values by the previous value, unfortunately, is not feasible under the current quantile-based format of the Forecast Hubs, as the growth rate of the $\alpha$-quantile may be different from the $\alpha$-quantile of the growth-rate. However, it may be an interesting approach if predictive samples are available or if quantiles for weekwise growth rates have been collected. Potentially, the variance stabilising time-series forecasting literature may be a useful source of other transformations for various forecast settings.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/illustration-effect-offset-log.png}
    \caption{Illustration of the effect of adding a small quantity to a value before taking the natural logarithm. For increasing x, all lines eventually approach the black line (representing a transformation with no offset applied).
    For a given solid line, the dashed line of the same colour marks the x-value that  is equal to 5 times the corresponding offset. It can be seen that for $a$ values smaller than one fifth of the transformed quantity, the effect of adding an offset is generally small. When choosing a suitable $a$, the trade-off is between staying close to the interpretation of a pure log-transformation (choosing a small $a$) and not giving excessive weights to small observations (by choosing a larger $a$, see Figure \ref{fig:HUB-log-different-offsets}).}
    \label{fig:illustration-effect-log-offset}
\end{figure}
